Efficient Handling of String-Number Conversion

### 2019-11-22 evaluation.tex

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, and Z3/Z3str3 on Basic String Constraint benchmarks.}
\scalebox{0.85}{
\begin{tabular}{|l r | r r r r r|}
\hline
\multicolumn{2}{|c}{}                   & {\tool} & CVC4  &Z3 & Z3-str3 & Trau+  \\ \hline
\multirow{3}{*}{PyEx}		& SAT      & 19586*   & 20123 & 18490 &  3514 & 19149 \\ 
							& UNSAT    &  3858*   &  3841 &  3855 &  4521 & 3828 \\
							& $\times$ &  1977*   &  1457 &  3076 & 17386 & 2444 \\ \hline
\multirow{3}{*}{APLAS}		& SAT      &   128*   &    51 &    19 &    52 & 132 \\
							& UNSAT    &   287*   &   214 &   100 &   118 & 82 \\
							& $\times$ &   185*   &   335 &   481 &   430 & 386 \\ \hline
\multirow{3}{*}{LeetCode}	& SAT      &   856*   &   871 &   881 &   651 & 778 \\
							& UNSAT    &  1784*   &  1785 &  1785 &  1787 & 1827 \\
							& $\times$ &    26*   &    10 &     0 &   228 & 61 \\ \hline
\multirow{3}{*}{StringFuzz}	& SAT      &   502*   &   610 &   316 &   605 & 688 \\
							& UNSAT    &   294*   &   255 &   206 &   217 & 339 \\
							& $\times$ &   269*   &   200 &   543 &   243 & 38 \\\hline
\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 16* & 11 &   12 &    10 & 247 \\
							& UNSAT    &   814*   &   818 &   807 &   778 & 500 \\
							& $\times$ &     5*   &     6 &    16 &    47 & 88 \\ \hline
\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13* & 9 &     6 &    16 & 311 \\
							& UNSAT    &  1030*   &  1025 &  1020 &   962 & 596 \\
							& $\times$ &     2*   &    11 &    19 &    67 & 138 \\ \hline
\multirow{3}{*}{Total} 		& SAT      & 21101*  &  21675 & 19724 &  4848 & 21305  \\
							& UNSAT    &  8067*  &   7938 &  7773 &  8383 & 7172  \\
							& $\times$ &  2464*  &  2019 &   4135 & 18401 & 3155  \\\hline	
\end{tabular}}
\label{table:base_benchmark}
\end{table}

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, and Z3/Z3str3 on Basic String Constraints + String-Number Conversion benchmark.}
\scalebox{0.8}{
\begin{tabular}{|l r | r r r r|}
\hline
\multicolumn{2}{|c}{}                   			& {\tool} & CVC4   &    Z3  & Z3-str3 \\ \hline
\multirow{3}{*}{String-Number-Leetcode}	 & SAT      &   2356*  &  1766 &  1025  &   333 \\ 
										 & UNSAT    &  16369*  & 15612 & 17234  & 15543 \\
										 & $\times$ &    202*  &  1549 &   668  &  3051 \\ \hline 
\multirow{3}{*}{String-Number-PythonLib} & SAT      &    912*  &   586 &  1802  &   389 \\ 
										 & UNSAT    &    720*  &   666 &   744  &   729 \\
										 & $\times$ &   1014*  &  1394 &   100  &  1528 \\ \hline
\multirow{3}{*}{String-Number-JavaScript}& SAT      &     20   &     5 &    16  &     4 \\ 
										 & UNSAT    &      0   &     0 &     0  &     0 \\
										 & $\times$ &      0   &    15 &     4  &    16 \\ \hline \hline
\multirow{3}{*}{Total}					 & SAT      &   3288*  &  2357 &  2843  &   726 \\ 
										 & UNSAT    &  17089*  & 16278 & 17978  & 16272 \\
										 & $\times$ &   1216*  &  2958 &   772  &  4595 \\ \hline
\end{tabular}}
\label{table:str_int_benchmark}
\end{table}

\begin{table}[h]
\centering
\caption{Comparison of {\tool}, CVC4, and Z3/Z3str3 with checkLuhn problems of 2 to 12 loops.}
\scalebox{0.9}{
\begin{tabular}{| c | c c c c|}
\hline
\# of Loops & {\tool} 	  &  CVC4    	 &       Z3   & Z3-str3 \\ \hline
2 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(0.27s)   & \textbf{SAT}(0.2s)  & $\times$ \\
3  			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(10.1s)  & \textbf{SAT}(0.1s)  & $\times$ \\
4 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(48.7s) &   $\times$  & $\times$ \\
5 			& \textbf{SAT}(<0.1s)  &  $\times$     &   $\times$  & $\times$ \\
6 			& \textbf{SAT}(0.16s)  &  $\times$     & \textbf{SAT}(0.13s) & $\times$ \\
7 			& \textbf{SAT}(0.24s)  &  $\times$     &   $\times$  & $\times$ \\
8 			& \textbf{SAT}(0.31s)  &  $\times$     & \textbf{SAT}(0.37s) & $\times$ \\
9 			& \textbf{SAT}(0.26s)  &  $\times$     &   $\times$  & $\times$ \\
10 			& \textbf{SAT}(0.21s)  &  $\times$     & \textbf{SAT}(0.53s) & $\times$ \\
11 			& \textbf{SAT}(0.23s)  &  $\times$     & \textbf{SAT}(0.37s) & $\times$ \\
12 			& \textbf{SAT}(0.33s)  &  $\times$     & \textbf{SAT}(0.40s) & $\times$ \\ \hline
\end{tabular}}
\label{table:checkLuhn}
\end{table}

@@

The results of the experiments are summarized in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}, respectively. Columns with heading \texttt{sat}/\texttt{unsat} show numbers of solved formulas. Columns with heading $\times$ indicate the number of instances the solver fails (including timeout, report unknown, report incorrect result, or crash). 
From Table~\ref{table:base_benchmark}, we can see that the performance  of {\tool} is as good as the most competitive tools such as CVC4 and Z3 on basic string constraints. In all of the benchmarks, {\tool} ranked either the 1st or the 2nd on the number of solved (SAT+UNSAT) cases. If we look into scrutiny, for the APLAS and StringFuzz benchmarks, there is a significant distance between {\tool} and the top-ranked tool on the SAT cases. But we believe this is not very important because both these two cases are artificial, either hand-crafted or randomly produced from a fuzzer. The more critical ones are those come from program analysis, which {\tool} has comparable performance to the best tool.

@@

>>>>

@@

The results of the experiments are summarized in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}, respectively. Columns with heading \texttt{sat}/\texttt{unsat} show numbers of solved formulas. Columns with heading $\times$ indicate the number of instances the solver fails (including timeout, report unknown, report incorrect result, or crash).

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, and Z3/Z3str3 on Basic String Constraint benchmarks.}
\scalebox{0.85}{
\begin{tabular}{|l r | r r r r r|}
\hline
\multicolumn{2}{|c}{}                   & {\tool} & CVC4  &Z3 & Z3-str3 & Trau+  \\ \hline
\multirow{3}{*}{PyEx}		& SAT      & 19586*   & 19763 & 18490 &  3514 & 19149 \\ 
							& UNSAT    &  3858*   &  3834 &  3855 &  4521 & 3828 \\
							& $\times$ &  1977*   &  1824 &  3076 & 17386 & 2444 \\ \hline
\multirow{3}{*}{APLAS}		& SAT      &   128*   &   205 &    19 &    52 & 132 \\
							& UNSAT    &   287*   &   221 &   100 &   118 & 82 \\
							& $\times$ &   185*   &   174 &   481 &   430 & 386 \\ \hline
\multirow{3}{*}{LeetCode}	& SAT      &   856*   &   859 &   881 &   651 & 778 \\
							& UNSAT    &  1784*   &  1785 &  1785 &  1787 & 1827 \\
							& $\times$ &    26*   &    22 &     0 &   228 & 61 \\ \hline
\multirow{3}{*}{StringFuzz}	& SAT      &   502*   &   671 &   316 &   605 & 688 \\
							& UNSAT    &   294*   &   240 &   206 &   217 & 339 \\
							& $\times$ &   269*   &   154 &   543 &   243 & 38 \\\hline
\multirow{3}{*}{cvc4\textsubscript{pred}} & SAT & 16* & 11 &   12 &    10 & 247 \\
							& UNSAT    &   814*   &   818 &   807 &   778 & 500 \\
							& $\times$ &     5*   &     6 &    16 &    47 & 88 \\ \hline
\multirow{3}{*}{cvc4\textsubscript{term}} & SAT & 13* & 8 &     6 &    16 & 311 \\
							& UNSAT    &  1030*   &   936 &  1020 &   962 & 596 \\
							& $\times$ &     2*   &   101 &    19 &    67 & 138 \\ \hline
\multirow{3}{*}{Total} 		& SAT      & 21101*  &  21517 & 19724 &  4848 & 21305  \\
							& UNSAT    &  8067*  &   7834 &  7773 &  8383 & 7172  \\
							& $\times$ &  2464*  &   2281 &   4135 & 18401 & 3155  \\\hline	
\end{tabular}}
\label{table:base_benchmark}
\end{table}

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, and Z3/Z3str3 on Basic String Constraints + String-Number Conversion benchmark.}
\scalebox{0.8}{
\begin{tabular}{|l r | r r r r|}
\hline
\multicolumn{2}{|c}{}                   			& {\tool} & CVC4   &    Z3  & Z3-str3 \\ \hline
\multirow{3}{*}{String-Number-Leetcode}	 & SAT      &   2356*  &  1543 &  1025  &   333 \\ 
										 & UNSAT    &  16369*  & 15676 & 17234  & 15543 \\
										 & $\times$ &    202*  &  1708 &   668  &  3051 \\ \hline 
\multirow{3}{*}{String-Number-PythonLib} & SAT      &    912*  &   408 &  1802  &   389 \\ 
										 & UNSAT    &    720*  &   660 &   744  &   729 \\
										 & $\times$ &   1014*  &  1578 &   100  &  1528 \\ \hline
\multirow{3}{*}{String-Number-JavaScript}& SAT      &     20   &     6 &    16  &     4 \\ 
										 & UNSAT    &      0   &     0 &     0  &     0 \\
										 & $\times$ &      0   &    14 &     4  &    16 \\ \hline \hline
\multirow{3}{*}{Total}					 & SAT      &   3288*  &  1957 &  2843  &   726 \\ 
										 & UNSAT    &  17089*  & 16336 & 17978  & 16272 \\
										 & $\times$ &   1216*  &  3300 &   772  &  4595 \\ \hline
\end{tabular}}
\label{table:str_int_benchmark}
\end{table}

From Table~\ref{table:base_benchmark}, we can see that the performance  of {\tool} is as good as the most competitive tools such as CVC4 and Z3 on basic string constraints. In all of the benchmarks, {\tool} ranked either the 1st or the 2nd on the number of solved (SAT+UNSAT) cases. If we look into scrutiny, for the APLAS and StringFuzz benchmarks, there is a significant distance between {\tool} and the top-ranked tool on the SAT cases. But we believe this is not very important because both these two cases are artificial, either hand-crafted or randomly produced from a fuzzer. The more critical ones are those come from program analysis, which {\tool} has comparable performance to the best tool.

@@

\begin{table}[h]
\centering
\caption{Comparison of {\tool}, CVC4, and Z3/Z3str3 with checkLuhn problems of 2 to 12 loops.}
\scalebox{0.9}{
\begin{tabular}{| c | c c c c|}
\hline
\# of Loops & {\tool} 	  &  CVC4    	 &       Z3   & Z3-str3 \\ \hline
2 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(0.66s) & \textbf{SAT}(0.2s)  & $\times$ \\
3  			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(1.78s) & \textbf{SAT}(0.1s)  & $\times$ \\
4 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(6.96s) &   $\times$  		& $\times$ \\
5 			& \textbf{SAT}(<0.1s)  &  \textbf{SAT}(17.2s) &   $\times$  		& $\times$ \\
6 			& \textbf{SAT}(0.16s)  &  $\times$  		  & \textbf{SAT}(0.13s) & $\times$ \\
7 			& \textbf{SAT}(0.24s)  &  $\times$    		  &   $\times$  		& $\times$ \\
8 			& \textbf{SAT}(0.31s)  &  $\times$   		  & \textbf{SAT}(0.37s) & $\times$ \\
9 			& \textbf{SAT}(0.26s)  &  $\times$    		  &   $\times$  		& $\times$ \\
10 			& \textbf{SAT}(0.21s)  &  $\times$    		  & \textbf{SAT}(0.53s) & $\times$ \\
11 			& \textbf{SAT}(0.23s)  &  $\times$    		  & \textbf{SAT}(0.37s) & $\times$ \\
12 			& \textbf{SAT}(0.33s)  &  $\times$     		  & \textbf{SAT}(0.40s) & $\times$ \\ \hline
\end{tabular}}
\label{table:checkLuhn}
\end{table}
